---
title: "Week 3 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))

cel <- drop_na(read_csv(url("https://www.dropbox.com/s/4ebgnkdhhxo5rac/cel_volden_wiseman%20_coursera.csv?raw=1")))

```

Following the directions on the Coursera assignment page, you will make four original visualizations. Note that the data for the CCES and CEL data are imported in code in the R Markdown file.

### Put your name here: WANG XIAOYUAN

## Exercise 1

Explain what you are visualizing here: the scatter plot of vote percentage won versus the seniority of MC for congress 115, I hypothesize that these two variables are positively correlated. I also use female variable to color the point and dem variable for facetting.
Put your figure here:

```{r exercise1,echo=FALSE}
cel$female<-recode(cel$female, '0'='male', '1'='female')
cel$dem<-recode(cel$dem, '0'='Republic', '1'='Democratic')

cel %>% filter(congress==115) %>% ggplot(aes(x=seniority, y=votepct, color=female)) +
  geom_point() +  
  geom_smooth(method="lm", se=FALSE) +
  facet_grid(~dem) +
  guides(col=guide_legend("Gender"))
  
```

## Exercise 2

Explain what you are visualizing here: The boxplot of vote percentage won for each party in congress 115

Put your figure here:

```{r exercise2,echo=FALSE}

cel$dem<-recode(cel$dem, '0'='Republic', '1'='Democratic')

cel %>% filter(congress==115) %>% ggplot(aes(x=dem, y=votepct, color=dem)) +
  geom_boxplot() + 
  scale_color_manual(values=c("blue","red"), name="Party") +
  labs(x="Party", y="vote percentage won")
  
```

## Exercise 3

Explain what you are visualizing here: The number of male and female MC for each party for congress 115

Put your figure here:

```{r exercise3,echo=FALSE}
library(ggthemes)
cel$female<-recode(cel$female, '0'='male', '1'='female')
cel$dem<-recode(cel$dem, '0'='Republic', '1'='Democratic')

cel %>% filter(congress==115) %>% group_by(dem, female) %>% summarise(num=n()) %>%
  ggplot(aes(x=dem, y=num, fill=female, label=num)) +
  geom_bar(stat="identity") +
  theme_wsj() +
  theme(legend.title =element_blank()) +
  labs(x="Party", y="number of MC", title="Number of MC by gender for Congress 115") +
  geom_text(position = position_stack(vjust = 0.5))

```

## Exercise 4

Explain what you are visualizing here: The number of MC from each party for all the congress, the x axis will be congress and y will be the number of MC from each party

Put your figure here:

```{r exercise4,echo=FALSE}
cel$dem<-recode(cel$dem, '0'='Republic', '1'='Democratic')

cel %>% group_by(congress, dem) %>% summarise(num=n()) %>%
  ggplot(aes(x=congress, y=num, color=dem)) +
  geom_line(size=1) +
  scale_color_manual(values=c("blue","red"), guide=FALSE) +
  labs(y="MC number", title="Number of MC from each party for all the congress") 


```
