---
title: "Data Review"
author: "WANG XIAOYUAN"
date: "25/8/2021"
output: html_document
---

```{r setup, include=FALSE}

#####Make sure you load any required packages.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Import Your Data

In the following code hunk, import your data.

```{r data_import}

data<-read.csv("../athlete_events.csv") 

```

## Part 1

For my first figure, I will user line plot to show the temporal change of sport events number for each Olympic Games, the x axis will be year and y axis will be number of sport events. There will be two lines, one for Summer Olympic Games and the other for Winter.

```{r data_1}
fig_dat1<-data %>% group_by(Year,Season) %>% summarise(event_count=n_distinct(Event))

####make sure you call the data so it will display in your report
fig_dat1

fig_dat1 %>% ggplot(aes(x=Year,y=event_count,color=Season)) + geom_line() +geom_point()
```

## Part 2

For my first figure, I will user bar chart to show the top3 country in gold leader board with the number of gold medals. The x axis will be year and y axis will be the country with most gold medal. 

```{r data_2}
fig_dat2<-data %>% filter(Medal=='Gold') %>% group_by(Year,Season, NOC) %>% summarise(Gold_Medal_count=n_distinct(Event)) %>% top_n(1, Gold_Medal_count) %>% arrange(desc(Gold_Medal_count))

fig_dat2

fig_dat2 %>% ggplot(aes(x=factor(Year), y=Gold_Medal_count, fill=NOC)) + 
  geom_bar(stat='identity',position =   position_dodge()) + 
  geom_text(aes(x=factor(Year), y=Gold_Medal_count/2,label=NOC),size=2, position =position_dodge(width=1)) +
  geom_text(aes(x=factor(Year), y=Gold_Medal_count*1.05,label=Gold_Medal_count),size=2, position =position_dodge(width=1)) +
  coord_flip() +
  facet_grid(.~Season, scale="free") +
  labs(x="Year",y="Gold Medals")
```


## Part 3

For my first figure, I will user scatter plot chart to show the number of athletes and number of gold medals for each SUmmer Olympic Games
```{r data_3}
sub_data1<-data %>% filter(Medal=='Gold') %>% group_by(Year,Season, NOC) %>% summarise(Gold_Medal_count=n_distinct(Event)) 

sub_data2<-data %>% group_by(Year,Season, NOC) %>% summarise(athletes_count=n_distinct(Name))

fig_dat3<-merge(sub_data2,sub_data1, by=c("Year","Season","NOC")) %>% filter(Season=="Summer")

fig_dat3

fig_dat3 %>% ggplot(aes(x=athletes_count, y=Gold_Medal_count)) + 
  geom_point() +
  labs(x="Number of athletes", y="Number of gold medal") + 
  facet_wrap(Year~.)
```


```{r data_3}
library(gganimate)

sub_data1<-data %>% filter(Medal=='Gold') %>% group_by(Year,Season, NOC) %>% summarise(Gold_Medal_count=n_distinct(Event)) 

sub_data2<-data %>% group_by(Year,Season, NOC) %>% summarise(athletes_count=n_distinct(Name))

fig_dat3<-merge(sub_data2,sub_data1, by=c("Year","Season","NOC"))

g<-fig_dat3 %>% ggplot(aes(x=athletes_count, y=Gold_Medal_count, color=NOC)) + 
  geom_point(alpha = 0.7) +
  facet_wrap(~Season) +
  theme(legend.position = 'none') +
  labs(title = 'Year: {frame_time}',x="Number of athletes", y="Number of gold medal") + 
  transition_time(Year) 

animate(g, 120, 4)
  
```